\begin{abstract_online}{International Visibility of ETDs in Portuguese and in English on a Brazilian Repository}{%
    \underline{Anna B Pavani}$^{1}$}{%
    }{%
    $^1$Pontifícia Universidade Católica do Rio de Janeiro, Brazil}
}

Background and Introduction: Portuguese is the 9th most spoken language (4th Western language) in the world according to Berlitz (https://www.berlitz.com/blog/most-spoken-languages-world) or the 8th (4th Western) according to Statista (https://www.statista.com/statistics/266808/the-most-spoken-languages-worldwide/). Both numbers indicate that Portuguese has a large number of speakers. The Comunidade de Países de Língua Portuguesa (https://www.cplp.org/) lists nine countries that have Portuguese as one of the official languages – Angola (36.7M), Brazil (216.4M), Cape Verde (0.6M), Guinea-Bissau (2.2M), Equatorial Guinea (1.7M), Mozambique (33.9M), Portugal (10.2M), São Tomé and Príncipe (0.2M), and Timor-Leste (1.4M). Their populations in 2023 were informed on Worldometer (https://www.worldometers.info/world-population/population-by-country/). It can easily be observed that Brazil holds 71.3\% of the Portuguese-speaking population. This work focuses on the ETD collection of a university in Brazil. It has offered graduate programs since the early 1960s, when theses and dissertations were published in Portuguese unless a special request was submitted. ETDs had been optional since 2000 and became mandatory in 2002. In 2008, ETDs presented in foreign languages started being accepted without special authorization. The current numbers of ETDs by language are:

Objectives: The objective of this work is to examine if the patterns of accesses (numbers of accesses and the numbers and languages of the countries where they originated) are different for ETDs in English and in Portuguese.

Method: This work is based on the analysis of data available on the Institutional Repository and organized in an open-access dataset available on the same repository. Data in the dataset include the numbers of ETDs and open-access ETDs, average numbers of partitions, numbers of accesses, and the countries from which they originated. The dataset shows that the percentages of ETDs in each language are very different. The percentages of ETDs in English are contained in the interval from a little less than 5.0% (2019) to a little over 8.0% (2023). The percentage of ETDs in English is growing every year, though. Examination of the statistics available on the repository shows that ETDs in English are predominantly in Science and Technology and Economics. For this reason, part of the analysis was based on averages to compensate for the differences in numbers. Normalization was also used due to the fact that ETDs are partitioned and the numbers of partitions vary according to the language and the year. Analysis is also performed on accesses from groups of countries that have either Portuguese or English as one of the official languages. The work contains tables and graphics.

Results and Conclusions: Most results are not surprising. The first is that accesses from Brazil account for almost 75\% of accesses to ETDs in Portuguese. The second is that accesses from the US are over 39\% for ETDs in English, and accesses from countries that have neither language as official are over 35\% and over 9\%, respectively, for English and Portuguese. The numbers of countries are between 150 and 172 for English and between 194 and 215 for Portuguese. It is important to remark that the numbers of ETDs in Portuguese are over 10 times larger than the corresponding numbers (per year) in English. A surprising result is the number of accesses from Portuguese-speaking countries, which were less than 7\% for ETDs in Portuguese. A not so surprising result is that in the five years of observation, the average numbers of accesses are different for both languages, but ETDs in Portuguese had two to three times the average numbers of accesses when compared to the works in English. There are differences in the patterns of accesses in the two sets. The percentages of accesses from Brazil are significant even for works in English. This is easy to explain due to the fact that the university is in Brazil. The other difference comes from the fact that ETDs in English are mostly in Science and Technology and Economics, and there are many repositories in these areas offering works in English.

\end{abstract_online}

