
    \begin{abstract_online}{A Pre-Processing Pipeline for Improved ETD Metadata Quality in Downstream Services}{%
    \underline{Elijah Chileshe}$^{1}$, Chilufya Chanda$^{1}$, Lighton Phiri$^{1}$}{%
    }{%
    $^1$ The University of Zambia, Zambia
}

Introduction: The Zambia National Electronic Theses and Dissertations (ZNETD) Portal serves as a crucial platform for accessing Electronic Theses and Dissertations (ETDs) from Higher Education Institutions (HEIs) in Zambia. The ZNETD functions by automatically harvesting ETD metadata from HEI Institutional Repositories (IRs) across Zambia. However, its usefulness is hindered by inconsistently formatted and poor-quality metadata. This paper outlines the core challenges surrounding metadata quality in the ZNETD Portal and proposes the implementation of a pre-processing pipeline to address these issues.

Motivation: There are a reported 10 IRs, of which eight (8) are presently functional (Chisale and Phiri, 2023). The HEIs with functional repositories generally have different ingestion policies and practices, resulting in inconsistently formatted metadata. More importantly, existing studies have revealed that some HEIs lack IR policies (Kasonde and Phiri, 2023).

Methodology: The work presented in this paper involved two (2) primary objectives:
Empirical evaluation of inconsistencies with ETD metadata from HEI IRs:—Metadata from HEIs with functional IRs was harvested using the Open Archives Initiative Protocol for Metadata Harvesting. The metadata elements were then analyzed in relation to the ETD-MS metadata standard.
Design and implementation of an ETD metadata preprocessing pipeline: —Pre-processing pipeline scripts were implemented to format metadata consistently and address the issue of incomplete metadata.

Anticipated Results: It is anticipated that the implementation of the pre-processing pipeline software tool will lead to a significant improvement in metadata quality within the Zambia National ETD Portal. Enhanced metadata consistency and completeness will facilitate more efficient resource discovery and retrieval, thereby enriching the user experience and maximizing the utility of the platform.

References:

Chisale, A., and Phiri, L. (2023, November 17). Towards Metadata Completeness in National ETD Portals for Improved Discoverability. http://ir.inflibnet.ac.in/handle/1944/2446

Kasonde, C. C., and Phiri, L. (2023). Assessing and Promoting Metadata Quality for Electronic Theses and Dissertations in Institutional Repositories Using a Policy-Driven Approach. INFLIBNET Centre, Gandhinagar.

Open Archives Initiative Protocol for Metadata Harvesting. (n.d.). Retrieved May 18, 2024, from https://www.openarchives.org/pmh

\end{abstract_online}

